\documentclass[a4paper]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\title{D \& D - Campaign: \\ Malidraxies}

\author{Adin Jasarevic}

\begin{document}


\begin{titlepage}
\maketitle
\end{titlepage}
\makeatletter
\renewcommand\thesection{}
\renewcommand\thesubsection{\@arabic\c@section.\@arabic\c@subsection}
\makeatother
\section{Introduction}
Malidraxies is a continent torn by chaos. The post-apocalyptic setting is a result of the war between the gods Vaxel god of death, and Vexil god of life. The aftermath of the war resulted in a magical fallout, and darkness has overtaken the world. The corruption slowly seeps across the planes and through the earth, only a few places are left unaffected by the disastrous transition. Most affiliated gods have been injured, some even left forgotten, and the world known to them has ended.\\ Subsequently the passage of time has left history soon to be buried, leaving only a glimpse of the past. With the world in ruins, civilisation has tried to adjust, but with the new world came the changes. Droughts, plagues and other disasters, were the least of people's worries, what came after was the most unnerving. In the beginning people thought nothing of it, but then it took a turn. It began as physical changes, one day you would wake up missing some teeth, or even discovering that your skin has lost all colour, but when madness spread, people were left horrified.\\
The surrounding continents of Phaalner, Grend, and Seramur have been trying to restrain the effects. Tirelessly searching for the cause of this catastrophe, while dooming the citizens of the once prospering continent to fend for themselves.\\
Society is now left intimidated and horrified by the prospect of adventuring and exploring. Only a few people are brave, or stupid enough to leave home following their intrepid dreams. But civilisation is in need of these morons. Not the treasures, stories, and achievements they leave home searching for, but the hope. Created by their sometimes shortsighted and rash decisions. Actions that could lead to a shift in this disaster that has left mankind baffled.
\newpage
\tableofcontents
\newpage

\section{1: History}
Nixera possesses a history brimming with strife, and has witnessed the fall of many eras.
\subsection{Prehistory}
In the beginning all was void. But from rips in the fabric of this realm radiance surfaced. The friction between these two created lacerations in space, and from these gashes the outer planes were created. These spiritual planes were the birthplaces of the first gods. It was here the first concepts of good and evil were conceptualized.\\
In the never-ending churning of the void another ripple was created. The void ripped into two pieces, both equally empty and desolate. The first piece was left unchanged. From the other piece, the elemental planes were created. Surrounded by the elemental chaos this plane fed on their elemental properties, and became the material plane.\\
The gods sought power from this realm, and sometimes these interactions had unseen consequences. Other planes were created, some corresponding to the gods nature. The Etherreal plane, Astral planes, and even the parallel planes such as the Feywild and the Shadowfell.\\
In an effort to stop the divide, the gods agreed to use mortals to settle their differences. This was the start of the Era of mankind. The mortals who sought strength from the gods, became their messengers, and some were even awarded immortality or near godhood. Mankind has since then been taken to the brink of destruction, and then reestablished many times. Many a time a god has strayed from their promise, interfering with the mortal plane, only time can tell what effect such occurrences will develop into.

\subsubsection{Before the war}
\textbf{More information will be open for you as you ask and learn about the properties of Nixera}
\\
Many thought the era before the war was one of peace and prosperity. On the surface this seemed to be true, but those that new better called it \textit{a cold war}. This was not long after Tiamat had been banished to the astral plane.
\subsection{The war}
Not much is known about the war. Only the effects of the drawn-out battle are clear.  
\subsubsection{Instigation}
Most say the war was grounded in the deep sibling rivalry between Vaxel and Vexil. Others think the war was instigated because of some sort of artefact, that lured the gods into action 
\section{2: The world}
Nixera is a large world with 5 continents
\subsection{Phaalner}
Is called the endless continent. Noone knows how much is left unexplored and many believe this land is endless.
\subsection{Grend}
is the largest and most eastern continent
\subsection{Seramur}
In elfish Seramur means land of the east, or land of desert-winds. Large parts of this continent are arid.
\subsection{Seramir}
In elfish Seramir means land of the west, or land of frozen heart. As supposed to the real world, because of Nixera's two suns there is only one cold pole on this plane.
\subsection{Malidraxies}

\section{3: The other planes}

\section{4: Character races}

\section{5: Character classes}

\section{6: Mutations}

\section{7: Magic}

\section{8: Equipment}

\section{9: Life in Nixera}

\section{10: Magic items}

\section{11: Monsters}
pelor ghourr
\end{document}